Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-05 manuscript-chicago-edited.tex
Add .tex version for submission

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Arab Spring}
\author{Megan Chiovaro\textsuperscript{1, 2}, Alexandra Paxton\textsuperscript{1,2,*}, \& Leah C. Windsor\textsuperscript{3,*}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Center for the Ecological Study of Perception and Action, University of Connecticut\\\textsuperscript{2} Department of Psychological Sciences, University of Connecticut\\\textsuperscript{3} University of Memphis\\\textsuperscript{*} Equal author contributions}
\authornote{

Correspondence concerning this article should be addressed to Megan Chiovaro, 406 Babbidge Road, Unit 1020, Storrs, CT 06269. E-mail: megan.chiovaro@uconn.edu}
\keywords{social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\usepackage{setspace}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

@@

\abstract{
In recent years, political activists have taken to social media platforms to
rapidly reach broad audiences. Despite the prevalence of micro-blogging in
these sociopolitical movements, the degree to which virtual mobilization
reflects or drives real-world movements is unclear. Here, we explore the
dynamics of real-world events and Twitter social cohesion in Syria during the
Arab Spring. Using the nonlinear methods cross-recurrence quantification
analysis and windowed cross-recurrence quantification analysis, we investigate
if frequency of events of different intensities are coupled with social
cohesion found in Syrian tweets. Results indicate that virtual social cohesion
is coupled with the counts of all and negative events each day but shows a
more nuanced connection to positive events, suggesting that virtual
mobilization does reflect real-world movements. We conclude with a discussion
of implications and applications of nonlinear methods in political science
research.
}

@@

@@

This work was completed in part as coursework done by lead author M. Chiovaro in
the \enquote{Applications of Nonlinear Time Series Analysis} graduate course at the
University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
Harrison).

@@

\leavevmode\hypertarget{ref-webber2005recurrence}{}%
---------. 2005. ``Recurrence Quantification Analysis of Nonlinear Dynamical Systems.'' \emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences} 94 (2005): 26--94.

@@

\leavevmode\hypertarget{ref-zeitzoff2017social}{}%
---------. 2017. ``How Social Media Is Changing Conflict.'' \emph{Journal of Conflict Resolution} 61 (9): 1970--91.

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Arab Spring}
\author{[author names redacted for blind review]\\ Word count : 10981}
\affiliation{\phantom{a}}
\keywords{social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\usepackage{setspace}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

@@

\abstract{In recent years, political activists have taken to social media platforms to
rapidly reach broad audiences. Despite the prevalence of micro-blogging in
these sociopolitical movements, the degree to which virtual mobilization
reflects or drives real-world movements is unclear. Here, we explore the
dynamics of real-world events and Twitter social cohesion in Syria during the
Arab Spring. Using the nonlinear methods cross-recurrence quantification
analysis and windowed cross-recurrence quantification analysis, we investigate
if frequency of events of different intensities are coupled with social
cohesion found in Syrian tweets. Results indicate that virtual social cohesion
is coupled with the counts of all and negative events each day but shows a
more nuanced connection to positive events, suggesting that virtual
mobilization does reflect real-world movements. We conclude with a discussion
of implications and applications of nonlinear methods in political science
research.
}

@@

This work is a reproducible manuscript. All code and analyses can be found at:
{[}redacted for blind review{]}.

@@

\noindent{[}redacted for blind review{]}

@@

\leavevmode\hypertarget{ref-webber2005recurrence}{}%
Webber Jr, Charles L and Zbilut, Joseph P. 2005. ``Recurrence Quantification Analysis of Nonlinear Dynamical Systems.'' \emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences} 94 (2005): 26--94.

@@

\leavevmode\hypertarget{ref-zeitzoff2017social}{}%
Zeitzoff, Thomas. 2017. ``How Social Media Is Changing Conflict.'' \emph{Journal of Conflict Resolution} 61 (9): 1970--91.
